Initial Analysis

### 2019-09-02 Initial_Analysis.Rmd
Updated the analysis to run the RFMO part on the Beast

1. Determine which countries have neighboring EEZs  
  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify neighboring polygons,
  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the neighboring data
2. Overlap distribution maps with neighbors data  
  2.1. For each species we merged the DBEM_Neighbors data with their known distribution (Gab's data)  
3. Determine transboundary if:  
  3.1. Species is present in both neighboring EEZs by INDEX

@@

## Sub Routine Estimating Neighbords

### Functions `EstNeighbors`

This function determines what EEZs are neighbors and returns a data.frame of it

```{r funEstNeighbors, eval = F, echo=T}
# Determine which countries are neighbors

EstNeighbors <- function(Shapefile){

@@

  # Build final data.frame substituting ID for name (in this case nc$name)
  Result_table = data.frame(Name = Shapefile$Name[mat[,1]], 
                            Neighbor_Territory = Shapefile$Name[mat[,2]]
  )

  # Remove duplicates... eg of course an object intersects with itself...
  Result_table = Result_table[Result_table$Name != Result_table$Neighbor_Territory,]

  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbors_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Name)

@@

  return(DBEM_Neighbors_Data)

@@

## Sub Routine

```{r Neighbords_Control_Pannel, eval = F, echo = F}

@@

subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru","Brazil"))
#### Grid cell information ####

@@

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  Neighbor_List <- EstNeighbors(World_EEZs)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

write.csv(Neighbor_List,
          paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""),
          row.names = F)

@@

### Function `GetSppDist`

@@

# Varibales needed
# Spp: Species to be analized, data with presence/absence per gridcell
# Index_EEZ: Reference list of all INDEX that fall within EEZs
# EEZ_Size: Number of grid-cells that each EEZ has
# Neighbors: Reference list of neighbouring countries

@@

#### For testing 
# Spp <- 600059
 #Model <- "All"
 #Neighbors <- Neighbor_List
 #Coord = CoorG
# __________________________________

# The function
EstTransIndex <- function(Spp,Model,Neighbors,Coord,Save="Y"){

@@

  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbors$INDEX,# Filter data only located within EEZs
           Model != "SAU_C") %>% # Only using observational and modelled data
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
    filter(Value > 0) %>%
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)
    ) %>%
    filter(Model_Index > 0) %>%
    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
    left_join(SppDist,
              by = c("TaxonKey","INDEX")) %>%
    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
           Value > 0) %>%
    mutate(Model_Index = Model_Index*100) %>%
    select(-Model, -Value, -Latitude,-Longitude) %>%
    left_join(EEZ_CellID,
              by = "INDEX") %>% 
    left_join(EEZIDs_List,
              by = "EEZID")

@@

  #Step 1.  Get EEZ id and neighbor
  Neighbors_EEZ <- Neighbors %>% 
    group_by(EEZID,Country_Territory,Neighbor_Territory) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    select(-n)

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(TaxonKey,
             Model_Index, # Un-comment after producing models x datasets
             EEZID) %>% 
    summarise(n_spp_eez = length(unique(INDEX))) %>% 
    left_join(Neighbors_EEZ,
              by = "EEZID") %>% 
    filter(Country_Territory %in% Trans_Spp$Name, #Filter out unwanted neighbors (those who don't have grids within but get included because they are neighbors)
           Neighbor_Territory %in% Trans_Spp$Name)

  # Step 3. Sum total grids per neighbors

  Neighbor_Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index,
      TaxonKey,n_spp_eez,
      Name=Neighbor_Territory, 
      Country_Territory
    )

  # Merge dataframes to get totals per neighbords
  Area_Index_D <- full_join(Country_Territory_T,
                            Neighbor_Territory_T, 
                            by = c("Model_Index","Name","TaxonKey")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per neighbors
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbor_Territory = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbor = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:3,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
    rename(Country_Territory = Name) %>% 
    full_join(Area_Index_D,
              by = c("TaxonKey","Country_Territory","Model_Index")
    ) %>% 
    filter(!is.na(Area_Index),
           !is.na(Model_Index) # Uncomment after producing Models x datasets
    )%>%  # Remove cases where the country does not pass the area_index and viceversa
    select(TaxonKey,Country_Territory,Neighbor_Territory,everything())

@@

@@

## Routine

```{r Control_Pannel, eval = T, echo = F}

@@

# Load neighbours data from previouse routine
Neighbor_List <- fread(paste(Data_Path,"Spatial_Data/Neighbor_List.csv", sep =""))

@@

@@

####_________________________________________ TESTING PERIOD_________________________________________####
## Species Test Data Just to know what's captured in these countries
#
# SAU_Data <- fread("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Catch_Data_Test/SAU_Catch_Data_Test.csv")
# #
# # #### Species per country
# #
# Spps <- SAU_Data %>%
#   filter(data_layer == "Reconstructed domestic catch") %>%
#   group_by(area_name,TaxonName = scientific_name) %>%
#   summarise(n()) %>%
#   left_join(Exploited_Species,
#             by = "TaxonName") %>%
#   filter(TaxonKey %in% Exploited_Species_List$TaxonKey)
#
# Exploited_Species_List <- Spps$TaxonKey

# Exploited_Species_List <- c("600006",600107)
# Exploited_Species_List = 600107
# TaxonKey <- unique(Spps$TaxonKey)

@@

# Spp_Trans <- NULL

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List, FUN = EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
    )
  )
)

@@

@@

# For Carmelia
Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))

@@

Auto_Remove_Territories <- Results_Trans %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Model_Index,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(1,2, 
    Neighbor_Territory = FishingRegion,
    Model_Index:CT_fishing_entity,
    NT_fishing_entity= fishing_entity,
    everything()) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

@@

Territories_to_Remove <- Results_Trans %>% 
  filter(
    Country_Territory %in% Islands_to_Remove |
      Neighbor_Territory %in% Islands_to_Remove |
      Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
      Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
      Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
      Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
      Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
      Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
      Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
      Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
      Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
      Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
      Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
      Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
      Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
      Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
      Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
      Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
      Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
      Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
      Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
      Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
      Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
      Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
      Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
      Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
      Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
      Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
      Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
  ) %>%
  group_by(Country_Territory,Neighbor_Territory) %>% 
  summarise(n())

# Cleaned results 
Clean_Results_Trans <- Auto_Remove_Territories %>% 
  anti_join(Territories_to_Remove,
            by = c("Country_Territory","Neighbor_Territory")
  ) %>% 
  filter(Same_Nation == "No")

# Load results for non transboundary (discrete) stocks
# Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))

@@

TenTwenyfive <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory)),
    Trans_Rate = n_trans/n_countries
    )
  # filter(Model_Index == 100)
  # head(Results_Data)

@@

Non_trans_Area_TenTwenyfive <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_no_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
  )

@@

Spp_Trans <- bind_rows(
    mclapply(
      600004, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
    )
  )

@@

  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbors$INDEX) %>% # Filter data only located within EEZs
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)) %>%
    filter(Model_Index > 0) %>%
    mutate(Model_Index = Model_Index*100) %>%
    left_join(Neighbors,
              by = "INDEX")

@@

Explore_Australia <- Australia %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  slice(1:20) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory)),
    )

@@

Neighbord_Territory_T <- Clean_Results %>% 
  group_by(eez_name=Neighbor_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name") %>% 
  select(Neighbor_Territory= eez_name,
         NT_fishing_entity=fishing_entity
         )

@@

EstNeighbors <- function(Shapefile){

>>>>

1. Determine which countries have Neighbouring EEZs  
  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify Neighbouring polygons,
  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the Neighbouring data
2. Overlap distribution maps with Neighbours data  
  2.1. For each species we merged the DBEM_Neighbours data with their known distribution (Gab's data)  
3. Determine transboundary if:  
  3.1. Species is present in both Neighbouring EEZs by INDEX

@@

## Sub Routine Estimating Neighbourds

### Functions `EstNeighbours`

This function determines what EEZs are Neighbours and returns a data.frame of it

```{r funEstNeighbours, eval = F, echo=T}
# Determine which countries are Neighbours

EstNeighbours <- function(Shapefile, Partial = "NA"){

@@

  # Build final data.frame substituting ID for name (in this case nc$name)
  Result_table = data.frame(Name = Shapefile$Name[mat[,1]], 
                            Neighbour_Territory = Shapefile$Name[mat[,2]]
  )

  # Remove duplicates... eg of course an object intersects with itself...
  Result_table = Result_table[Result_table$Name != Result_table$Neighbour_Territory,]

  if(Partial == T){
    # If only partial analysis just returns Neighbour list
    return(Result_table)

  }else{
  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbours_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Name)

@@

  return(DBEM_Neighbours_Data)

  } # end ifelse
} # end function

# subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru"))
# EstNeighbours(subset)
# EstNeighbours(subset,T)

@@

### Sub Routine

#### EEZ

```{r EEZ_Neighbourds_Control_Pannel, eval = F, echo = F}

@@

#### Grid cell information ####

@@

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  EEZ_Neighbour_List <- EstNeighbours(World_EEZs, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

write.csv(EEZ_Neighbour_List,
          paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.csv", sep =""),
          row.names = F)

@@

#### RFMO

```{r RFMO_Index, eval = F, echo = F}

# SAU RFMO shapefile

# The path
path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s) %>% 
  st_set_crs(3832) %>% # Making sure is same proyection
  st_transform(3832) # to match shapefiles

# Load coordinate system

Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# COnvert Coor system to sf
Coor_sf = st_as_sf(Coor,
                        coords = c("Longitude", "Latitude")) %>% 
  st_set_crs(3832) %>% # to match shapefiles
  st_transform(3832) # to match shapefiles

# Merge RFMO and coor datasets
RFMO_Coor <- st_join(RFMOs_sf,
                         Coor_sf,
                         join = st_contains) %>% 
  filter(!is.na(INDEX)) # Remove regions beyond RFMOs

# head(RFMO_Coor)

# Convert it back to a data frame and select only the two columns we want
RFMO_INDEX <- as.data.frame(RFMO_Coor) %>% 
  select(INDEX,Name) %>% 
  arrange(INDEX)

# head(RFMO_INDEX)

# Save new data
write.csv(RFMO_INDEX,
          paste(Data_Path,"Spatial_Data/RFMO/RFMO_INDEX.csv",sep=""),
          row.names = F
          )

# Map it (works!)

# RFMO_INDEX %>%
#   left_join(Coor,
#             by = "INDEX") %>%
#   ggplot(.,
#             aes(x = Longitude,
#                 y = Latitude,
#                 color = Territory,
#                 fill = Territory)
#             ) +
#   geom_tile() 
# 
# 
# RFMO_INDEX %>%
#   left_join(Coor,
#             by = "INDEX") %>%
#   ggplot(.,
#             aes(x = Longitude,
#                 y = Latitude,
#                 color = INDEX,
#                 fill = INDEX)
#             ) +
#   geom_tile() +
#   facet_wrap(~Territory)

```{r RFMO_Neighbourds_Control_Pannel, eval = F, echo = F}

# SAU RFMO shapefile

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s)

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  RFMO_Neighbour_List <- EstNeighbours(RFMOs_sf, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

 ## Include Index column

RFMO_Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbour_List.csv",sep=""),header = TRUE) %>% 
  left_join(RFMO_INDEX,
            by = "Name") %>% 
  rename(Territory = Name,
         Neighbour = Neighbour_Territory)

# head(RFMO_Neighbour_List)

write.csv(RFMO_Neighbour_List,
          paste(Data_Path,"Spatial_Data/RFMO_Neighbour_List.csv", sep =""),
          row.names = F)

```
### Function `GetSppDist`

@@

# Varibales needed
# Spp: Species to be analized, data with presence/absence per gridcell
# Index_EEZ: Reference list of all INDEX that fall within EEZs
# EEZ_Size: Number of grid-cells that each EEZ has
# Neighbours: Reference list of neighbouring countries

@@

#### For testing 
# Spp <- #600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG

# For EEZ
 # Neighbours <- Neighbours_EEZ
 # Index_Code <- EEZ_Index_Code

 # For RFMO 
 # Index_Code <- RFMO_INDEX
 # Neighbours <- RFMO_Neighbor_List %>% 
 #   rename(Territory = Name,
 #         Neighbour = Neighbor_Territory)

# __________________________________
# __________________________________

# The function
EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){

@@

  #____________ ESTIMATING MODEL INDEX (TRESHOLD 1)_________ #
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
           Model != "SAU_C") %>% # Only using observational and modelled data
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  
    filter(Value > 0) %>%
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)
    ) %>%
    filter(Model_Index > 0) %>%
    # ____________ ESTIMATING FUNDAMENTAL NICHE (TRESHOLD 2)_________ #
    left_join(SppDist,
              by = c("TaxonKey","INDEX")) %>%
    filter(Model == "SAU_C", # Only keeping cells where SAU catch exists
           Value > 0) %>%
    mutate(Model_Index = Model_Index*100) %>%
    select(-Model, -Value, -Latitude,-Longitude) %>%
    left_join(Index_Code,
              by = "INDEX")

  # MODEL INDEX (TRESHOLDS 1 & 2) #
  Model_Index_D <- Trans_Spp %>% 
    group_by(Territory,
             TaxonKey,
             Model_Index
    ) %>% 
    summarise(n_cells_spp = n()) %>% 
    select(-n_cells_spp)

@@

  #Step 1.  Get EEZ id and Neighbour
  Neighbours_List <- Neighbours %>% 
    group_by(Territory,Neighbour) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    select(-n)

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(TaxonKey,
             Model_Index, # Un-comment after producing models x datasets
             Territory) %>% 
    summarise(n_spp_eez = length(unique(INDEX))) %>% 
    left_join(Neighbours_List,
              by = "Territory") %>% 
    filter(Territory %in% Trans_Spp$Territory, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
           Neighbour %in% Trans_Spp$Territory)

  # Step 3. Sum total grids per Neighbours

  # Split dataframes to merge latter
  Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index, # Un-comment after producing models x datasets
      TaxonKey,
      Name=Territory,
      n_spp_eez
    )

  Neighbour_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      Model_Index,
      TaxonKey,n_spp_eez,
      Name=Neighbour, 
      Territory
    )

  # Merge dataframes to get totals per Neighbourds
  Area_Index_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Model_Index","Name","TaxonKey")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbour = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:3,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
    # rename(Territory = Name) %>% 
    full_join(Area_Index_D,
              by = c("TaxonKey","Territory","Model_Index")
    ) %>% 
    filter(!is.na(Area_Index),
           !is.na(Model_Index) # Uncomment after producing Models x datasets
    ) %>%  # Remove cases where the country does not pass the area_index and viceversa
    select(TaxonKey,Territory,Neighbour,everything())

@@

# __________________________________
# Test function
# __________________________________
# EstTransIndex(Spp = 600107,
#               Mode = "All",
#               Neighbours = ,Coord,Index_Code,Save="Y")
# 
# Spp <-  # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG
# 
# # For EEZ
#  # Neighbours <- Neighbours_EEZ
#  # Index_Code <- EEZ_Index_Code
#  
#  # For RFMO 
#  Index_Code <- RFMO_INDEX
#  Neighbours <- RFMO_Neighbor_List %>% 
#    rename(Territory = Name,
#          Neighbour = Neighbor_Territory)

@@

## Routine for estimating transboundary species

```{r EEZ_Control_Pannel, eval = T, echo = F}

# Set Jurisdiction to EEZ or RFMO
Jurisdiction <- "EEZ"

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")

@@

# Load Jursidiction-dependant data
if(Jurisdiction == "EEZ"){
  # Load neighbours data from previouse routine
  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.csv", sep =""))

@@

  Index_Code <- EEZIDs_List %>% 
    left_join(EEZ_CellID) %>% 
    rename(Territory = Name)

  # Load neighbours data from previouse routine
  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbours_List.csv", sep =""))

  Index_Code <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Index_Code.csv", sep =""))

@@

# Just a warning for me not to forget
print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level"))
```

@@

# Run model in parallel
system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List,
      FUN = EstTransIndex,
      Model = "All", # all data sources
      Neighbours = Neighbours_Data,
      Coord = CoorG,  # Gabriels coordinate system for read species dist
      Index_Code = Index_Code, 
      Save = "Y",  # For saving
      Jurisdiction_Type = Jurisdiction # For saving in proper path
    )
  )
)

@@

## Function `GetTransResults`

@@

# For Carmelia
if(Sys.info()[7] == "carmelia"){
  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
}else{

@@

  Auto_Remove_Territories <- Results_Trans %>%   
    rename(FishingRegion=Country_Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Country_Territory= FishingRegion,
           FishingRegion=Neighbour_Territory,
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour_Territory = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour_Territory),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

  Territories_to_Remove <- Results_Trans %>% 
    filter(
      Country_Territory %in% Islands_to_Remove |
        Neighbour_Territory %in% Islands_to_Remove |
        Country_Territory == "Balearic Island (Spain)" & Neighbour_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
        Country_Territory == "British Virgin Isl. (UK)" & Neighbour_Territory == "Anguilla" |
        Neighbour_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
        Country_Territory == "Corsica (France)" & Neighbour_Territory == "France (Mediterranean)" |
        Neighbour_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
        Country_Territory == "Crete (Greece)" & Neighbour_Territory == "Grece" |
        Neighbour_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
        Country_Territory == "Cyprus (North)" & Neighbour_Territory == "Cyprus (South)" |
        Neighbour_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
        Country_Territory == "Channel Isl. (UK)" & Neighbour_Territory == "United Kingdom" |
        Neighbour_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
        Country_Territory == "Glorieuse Islands (France)" & Neighbour_Territory == "Mayotte (France)" |
        Neighbour_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
        Country_Territory == "Guam (USA)" & Neighbour_Territory == "Northern Marianas (USA)" |
        Neighbour_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
        Country_Territory == "Italy" & Neighbour_Territory == "Sardinia (Italy)" |
        Neighbour_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
        Country_Territory == "Italy" & Neighbour_Territory == "Sicily (Italy)" |
        Neighbour_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (main islands)"|
        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (Ogasawara Islands)"|
        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
        Country_Territory == "Norway" & Neighbour_Territory == "Svalbard Isl. (Norway)" |
        Neighbour_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
        Country_Territory == "Sicily (Italy)" & Neighbour_Territory == "Sardinia (Italy)" |
        Neighbour_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
        Country_Territory == "South Africa (Atlantic Coast)" & Neighbour_Territory == "South Africa (Indian Ocean Coast)" |
        Neighbour_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
        Country_Territory == "USA (Alaska, Arctic)" & Neighbour_Territory == "USA (Alaska, Subarctic)" |
        Neighbour_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Country_Territory,Neighbour_Territory) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results_Trans <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Country_Territory","Neighbour_Territory")
    ) %>% 
    filter(Same_Nation == "No")

} # closes ifstatement for carmelia temporal files
# Load results for non transboundary (discrete) stocks
# Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))

@@

Transboundary_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbour_Territory)),
    Trans_Rate = n_trans/n_countries
    )
  # filter(Model_Index == 100)
  # head(Results_Data)

@@

Discrete_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_no_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbour_Territory))
  )

## Validate Results using RFMOs

```{Validation_RFMOs}

#### Load RFMO data provided by Vicky (SAU)

RFMOs_sf <- fread(paste(Data_Path,"Spatial_Data/SAU_RFMO/SAU_RFMO_Sept_2015.shp",sep=""))

@@

Spp_Trans <- bind_rows(
    mclapply(
      600004, FUN =EstTransIndex, Model = "All", Neighbours = Neighbour_List, Coord = CoorG
    )
  )

@@

  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Neighbours$INDEX) %>% # Filter data only located within EEZs
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)) %>%
    filter(Model_Index > 0) %>%
    mutate(Model_Index = Model_Index*100) %>%
    left_join(Neighbours,
              by = "INDEX")

@@

Explore_Australia <- Australia %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  slice(1:20) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbour_Territory)),
    )

@@

Neighbourd_Territory_T <- Clean_Results %>% 
  group_by(eez_name=Neighbour_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name") %>% 
  select(Neighbour_Territory= eez_name,
         NT_fishing_entity=fishing_entity
         )

@@

EstNeighbours <- function(Shapefile){
